Roster Review (Generic)

### 2019-08-19 rosterReview_generic.Rmd
Latest rosters, expanded free agent look

rosters %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 3)) %>% 
  arrange(zar %>% desc) %>% 
  mutate(zar = zar %>% round(digits=1)) %>% 
  select(team, name_full, positions, type, zar) %>% 
  View("Available Free Agents")
```

>>>>

free_agent_compare <- 
  rosters %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 3)) %>% 
  arrange(zar %>% desc) %>% 
  mutate(zar = zar %>% round(digits=1))

free_agent_compare %>% 
  # select(team, name_full, positions, type, zar) %>% 
  select(team, name_full, positions, type, zar, g:war, z_r:z_whip)
  View("Available Free Agents Expanded")

free_agent_compare %>% 
  select(team, name_full, positions, type, zar) %>%
  View("Available Free Agents")
```
